---
title: "2022_04_04-OperonMapper-Operons_in_scaffold"
author: "Mirna Vazquez Rosas Landa"
date: "4/5/2022"
output: html_document
---
# Operon Mapper 

- I used [OperonMapper](https://biocomputo.ibt.unam.mx/operon_mapper/)  to predict the genes that are near the **CALIN** element predicted.

# Operon Mapper output

The output files from Operon Mapper are:

- predicted_protein_sequences_417647
- predicted_orfs_417647
- predicted_COGs_417647
- operonic_gene_pairs_417647
- **list_of_operons_417647**
- functional_descriptions_417647
- ORFs_coordinates_417647

The **list_of_operons_417647** file contains the annotation of the elements and the number of operons predicted. 

Exploring the **list_of_operons_417647** file.

```{r  echo=TRUE,message=FALSE, warning=FALSE}
library(tidyverse)
Operon_mapper<-read_delim("../data/417647/list_of_operons_417647", delim="\t") %>%
  fill(Operon) # Fill NA values with the previous value in a column
```

By manually looking at the **list_of_operons_417647** file I found a equence that is associated to a transposase is [COG2826](https://www.ncbi.nlm.nih.gov/research/cog/cog/COG2826/), and was found in the **qb307082014_I_scaffold_18** scaffold. Suggesting is the one infered by **Integron Finder**.

```{r  echo=TRUE, message=FALSE, warning=FALSE}
COG2826<-read_delim("../data/417647/list_of_operons_417647", delim="\t") %>%
  fill(Operon) %>%
  drop_na(Type) %>%
  filter(COGgene == "COG2826")
```

I look at the operons that where up and down to see which genes would be there and I found something interesting.

```{r  echo=TRUE, message=FALSE, warning=FALSE}
operons_to_look<-c("7", "9")
neighbour_genes<-read_delim("../data/417647/list_of_operons_417647", delim="\t") %>%
  fill(Operon) %>%
  drop_na(Type) %>%
  filter(Operon %in% operons_to_look)
```

- The gene in operon 9 has a non identidied function, I extracted the sequence and make a web blast search.
